---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pactaverse

<!-- badges: start -->
[![R-CMD-check](https://github.com/RMI-PACTA/pactaverse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/RMI-PACTA/pactaverse/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/RMI-PACTA/pactaverse/branch/main/graph/badge.svg)](https://app.codecov.io/gh/RMI-PACTA/pactaverse?branch=main)
<!-- badges: end -->

The goal of pactaverse is to provide and easy way to load and install all PACTA 
packages. 

## Installation

You can install the development version of pactaverse like so:

``` r
# Install the development version from GitHub
# install.packages("pak")
pak::pak("RMI-PACTA/pactaverse")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pactaverse)
## basic example code
```

## Code of Conduct

Please note that the pactaverse project is released with a [Contributor Code of Conduct](https://rmi-pacta.github.io/pactaverse/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
